### 2016-01-31 inputs/introduction.tex
phrasing, references

as high as 0.84-0.94 (measured as $R^{2}$ between true and imputed genotypes). Imputation of missing GBS data without alignment to the reference genome has been reported in alfalfa (``Medicago sativa'', \cite{Rocher_validation_2015}) and red raspberry (``Rubus idaeus'', \cite{ward_2013_saturated}).\\

>>>>

as high as 0.84-0.94 (measured as $R^{2}$ between true and imputed genotypes). Imputation of missing GBS data without alignment to the reference genome has been reported in alfalfa (``Medicago sativa'', \cite{Rocher_validation_2015}) and red raspberry (``Rubus idaeus'', \cite{ward_saturated_2013}).\\

### 2016-01-31 inputs/materials_and_methods.tex
phrasing, references

A further quality filter, implemented through ad-hoc Python scripts, removed heterozygous loci with less than 4 and homozygous loci with less than 11 aligned reads. A similar filtering was performed in \cite{Rocher_validation_2015} using less restrictive thresholds. Alfalfa is an autotetraploid plant species and can therefore present three different heterozygous genotypes: AAAB, AABB and ABBB. Sequencing depth in this study was not sufficient for accurate tetraploid allelic dosage, but following \cite{li_saturated_2014} and \cite{li_genomic_2015} reliable genotype calls based on diploid allelic dosage were obtained considering diploid heterozygotes (i.e. AB), while the two homozygous genotypes (AAAA and BBBB) were considered diploid homozygotes (i.e., AA or BB).

@@

\subsection{Imputation methods}
\label{sec:imputation_methods}
We considered six imputation methods: Mean Value Imputation (MNI), K-Nearest Neighbour Imputation (KNNI), Random Forest Imputation (RFI), Singular Value Decomposition Imputation (SVDI), Localized Haplotype Clustering Imputation (``Beagle'') and the ``FILLIN'' algorithm from the ``Tassel'' programming suite \cite{swarts_novel_2014}. For all algorithms, we imputed a $m\times n$ matrix of m individuals and n markers whose data points, defined in the set \{0,1,2,NA\}, represented the three possible genotypes (AA, AB, and BB) and the missing value, respectively. 
\paragraph{MNI}
\label{par:MNI}
: in Mean Value Imputation each missing data point was simply replaced by the mean of the non-missing values for that marker, which was then discretized to the closest value in \{0,1,2\}. 
\paragraph{KNNI}
\label{par:KNNI}
: in K-Nearest Neighbors Imputation, missing data points were imputed based on the weighted average of the K closest markers \cite{troyanskaya_missing_2001}. This K-neighbourhood was defined by the Simple Matching Coefficient distance function \cite{schwender_statistical_2007}, specifically designed for categorical data. $K=4$ was used in KNNI, and neighbour values were weighted by the reciprocal of their distance from the data point to be imputed.
\paragraph{SVDI}
\label{par:SVDI}
: Singular Value Decomposition (SVD) imputation was based on the following factorization of the genotype matrix M (m markers, n individuals):

>>>>

Alfalfa is an autotetraploid plant species and can therefore present three different heterozygous genotypes: AAAB, AABB and ABBB. Sequencing depth in this study was not sufficient for accurate tetraploid allelic dosage, but following \cite{li_saturated_2014} and \cite{li_genomic_2015} reliable genotype calls based on diploid allelic dosage were obtained considering diploid heterozygotes (i.e. AB), while the two homozygous genotypes (AAAA and BBBB) were considered diploid homozygotes (i.e., AA or BB). A further quality filter, implemented through ad-hoc Python scripts, removed heterozygous loci with less than 4 and homozygous loci with less than 11 aligned reads. A similar filtering was performed in \cite{Rocher_validation_2015} using less restrictive thresholds.

@@

\subsection{Imputation methods}
\label{sec:imputation_methods}
We considered six imputation methods: Mean Value Imputation (MNI), K-Nearest Neighbour Imputation (KNNI), Random Forest Imputation (RFI), Singular Value Decomposition Imputation (SVDI), Localized Haplotype Clustering Imputation (``Beagle'') and the ``FILLIN'' algorithm from the ``Tassel'' programming suite. For all algorithms, we imputed a $m\times n$ matrix of m individuals and n markers whose data points, defined in the set \{0,1,2,NA\}, represented the three possible genotypes (AA, AB, and BB) and the missing value, respectively. 
\paragraph{MNI}
\label{par:MNI}
: in Mean Value Imputation each missing data point was simply replaced by the mean of the non-missing values for that marker, which was then discretized to the closest value in \{0,1,2\}. 
\paragraph{KNNI}
\label{par:KNNI}
: in K-Nearest Neighbors Imputation, missing data points were imputed based on the weighted average of the K closest markers \cite{troyanskaya_missing_2001}. This K-neighbourhood was defined by the Simple Matching Coefficient distance function \cite{schwender_statistical_2007}, specifically designed for categorical data. $K=4$ was used in KNNI, and neighbour values were weighted by the reciprocal of their distance from the data point to be imputed.
\paragraph{SVDI}
\label{par:SVDI}
: Singular Value Decomposition (SVD) imputation was based on the following factorization of the genotype matrix M (m markers, n individuals):
